---
title: "LaLonde Lab — Day 1 Solution (R)"
subtitle: "NSW experimental panel · DiD by hand and by regression"
author: "Zurich Workshop · May 2026"
format:
  html:
    theme: cosmo
    toc: true
    code-fold: false
    embed-resources: true
  pdf:
    toc: true
    documentclass: article
    geometry: margin=1in
engine: knitr
execute:
  echo: true
  warning: false
  message: false
---

# Setup

Load the experimental panel from the Mixtape-Sessions GitHub. Three years per person: `74`, `75`, `78`. Outcome: real earnings. Treatment: `ever_treated`.

```{r}
library(haven)
library(dplyr)
library(tidyr)
library(fixest)
library(broom)

exp_panel <- read_dta(
  "https://raw.github.com/Mixtape-Sessions/Causal-Inference-2/master/Lab/Lalonde/lalonde_exp_panel.dta"
)

glimpse(exp_panel)
```

------------------------------------------------------------------------

# Part 1 — The 2×2 by hand

Use `78` as the post period and `75` as the pre period.

```{r}
cells <- exp_panel |>
  filter(year %in% c(75, 78)) |>
  group_by(ever_treated, year) |>
  summarise(re_mean = mean(re), .groups = "drop")

cells
```

The four cell means:

```{r}
Y_T_75 <- cells$re_mean[cells$ever_treated == 1 & cells$year == 75]
Y_T_78 <- cells$re_mean[cells$ever_treated == 1 & cells$year == 78]
Y_C_75 <- cells$re_mean[cells$ever_treated == 0 & cells$year == 75]
Y_C_78 <- cells$re_mean[cells$ever_treated == 0 & cells$year == 78]

cat(sprintf("Y_T_75 = %8.2f\n", Y_T_75))
cat(sprintf("Y_T_78 = %8.2f\n", Y_T_78))
cat(sprintf("Y_C_75 = %8.2f\n", Y_C_75))
cat(sprintf("Y_C_78 = %8.2f\n", Y_C_78))
```

The DiD:

```{r}
DiD_hand <- (Y_T_78 - Y_T_75) - (Y_C_78 - Y_C_75)
cat(sprintf("\nDiD by hand: %.2f\n", DiD_hand))
```

The post-period difference in means (also valid under randomization):

```{r}
post_dim <- Y_T_78 - Y_C_78
cat(sprintf("Post-period diff-in-means: %.2f\n", post_dim))
```

**Expected values on this panel** (cell means: $Y^T_{75} = 1532$, $Y^T_{78} = 6349$, $Y^C_{75} = 1267$, $Y^C_{78} = 4555$, $n_T = 185$, $n_C = 260$):

-   Post-period diff-in-means: **\$1,794** (the standard D&W benchmark)
-   DiD with 75 as pre: **\$1,529**

They disagree by \$265 because the pre-period had +\$265 of random imbalance (treated happened to earn more in 75). Random assignment guarantees $\mathbb{E}[\widehat\delta] = \text{ATT}$ in expectation across re-randomizations — not in any one realization. **Unbiasedness is a repeated-sampling concept.**

------------------------------------------------------------------------

# Part 2 — The three regressions

Restrict to `year ∈ {75, 78}`. Each spec should return the same DiD coefficient.

```{r}
df <- exp_panel |>
  filter(year %in% c(75, 78)) |>
  mutate(post = as.integer(year == 78))
```

### Regression 1 — OLS with interactions

```{r}
reg1 <- lm(re ~ ever_treated * post, data = df)
summary(reg1)$coefficients
```

The coefficient on `ever_treated:post` is your DiD.

### Regression 2 — TWFE

```{r}
reg2 <- feols(re ~ ever_treated:post | id + year, data = df, vcov = "hetero")
summary(reg2)
```

### Regression 3 — Long differences

```{r}
df_wide <- exp_panel |>
  filter(year %in% c(75, 78)) |>
  select(id, ever_treated, year, re) |>
  pivot_wider(names_from = year, values_from = re, names_prefix = "re") |>
  mutate(d_re = re78 - re75)

reg3 <- lm(d_re ~ ever_treated, data = df_wide)
summary(reg3)$coefficients
```

All three return **\$1,529** (the DiD on this sample).

------------------------------------------------------------------------

# Part 3 — Event study

Include `74`. Baseline is `75` (omitted).

```{r}
es <- feols(re ~ i(year, ever_treated, ref = 75) | id + year,
            data = exp_panel,
            vcov = ~id)

es_pts <- tidy(es, conf.int = TRUE) |>
  mutate(year_num = readr::parse_number(term))

es_pts
```

Plot:

```{r}
#| fig-width: 7
#| fig-height: 4
library(ggplot2)

bind_rows(
  tibble(year_num = 75, estimate = 0, conf.low = 0, conf.high = 0),
  es_pts |> select(year_num, estimate, conf.low, conf.high)
) |>
  ggplot(aes(year_num, estimate)) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "grey50") +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.15) +
  geom_point(size = 3) +
  scale_x_continuous(breaks = c(74, 75, 78)) +
  labs(x = NULL, y = "Coefficient (re difference vs. 1975 baseline)",
       title = "Event study: NSW experimental panel") +
  theme_minimal(base_size = 12)
```

------------------------------------------------------------------------

# Part 4 — Event study by hand

Each coefficient is a 2×2 DiD with `75` as baseline.

```{r}
cell <- function(yr, trt) {
  exp_panel |> filter(year == yr, ever_treated == trt) |> pull(re) |> mean()
}

beta_74 <- (cell(74, 1) - cell(75, 1)) - (cell(74, 0) - cell(75, 0))
beta_78 <- (cell(78, 1) - cell(75, 1)) - (cell(78, 0) - cell(75, 0))

cat(sprintf("Hand-computed beta_74 = %.2f\n", beta_74))
cat(sprintf("Hand-computed beta_78 = %.2f\n", beta_78))
```

These should match the regression coefficients from Part 3 to machine precision.

------------------------------------------------------------------------

# Part 5 — Interpretation

-   `beta_78 = $1,529` is the post-period treatment effect — statistically distinguishable from zero. The NSW program *worked* on this sample.
-   `beta_74 ≈ -$277` is the pre-treatment placebo. Small relative to `beta_78` and not significant. **Pre-trend gut check passes.**
-   The DiD (\$1,529) and the post-period diff-in-means (\$1,794) **don't match** in this sample. Both are valid estimators of the ATT; they disagree by \$265 because of finite-sample pre-period imbalance. Under random assignment they agree *in expectation* — unbiasedness is a repeated-sampling concept, not a property of any single realization.

------------------------------------------------------------------------

# What we did, in one paragraph

We took the experimental NSW panel — the *clean* version of the LaLonde data, restricted by Dehejia & Wahba to men with two years of pre-program earnings ($n_T = 185$, $n_C = 260$). The post-period difference-in-means is **\$1,794** — the standard D&W RCT benchmark. The DiD using 75 as pre-period is **\$1,529**, because in this particular sample the pre-period had +\$265 of random imbalance. Both estimators are unbiased under random assignment; they disagree by \$265 in this one realization. Three regression specifications (OLS with interactions, TWFE, long differences) all return the DiD of \$1,529 to machine precision. The event study gives $\beta_{74} \approx -\$277$ (passes the pre-trend gut check) and $\beta_{78} = +\$1,529$ (same as the DiD by construction).

------------------------------------------------------------------------

# Part B — Now make it harder (covariates lab)

Switch to the non-experimental panel: same 297 NSW treated men, but the controls are replaced with a random sample from the CPS. Selection is severe and negative.

```{r}
nonexp_panel <- read_dta(
  "https://raw.github.com/Mixtape-Sessions/Causal-Inference-2/master/Lab/Lalonde/lalonde_nonexp_panel.dta"
)

# Naive DiD — should give the wrong sign
df_ne <- nonexp_panel |>
  filter(year %in% c(75, 78)) |>
  mutate(post = as.integer(year == 78))

naive_did <- lm(re ~ ever_treated * post, data = df_ne)
coef_naive <- coef(naive_did)[["ever_treated:post"]]
cat(sprintf("Naive DiD on non-experimental panel: %.2f\n", coef_naive))
# Expected: +3,621
# Right sign, wrong magnitude — overshoots the $1,794 benchmark by ~$1,800
# because NSW men had unusually low pre-earnings ($1,532) and bounced back fast
# while CPS controls were stable. DiD attributes the differential growth to treatment.
```

## DiD with additive X (Scott's published spec)

This is what `lalonde-did-stata.do` actually runs: pooled OLS on all three years, X enters additively (no Post × X interactions), no fixed effects.

```{r}
df_ne_all <- nonexp_panel  # keep all three years
df_ne_all$post <- as.integer(df_ne_all$year == 78)

X_vars <- c("age", "agesq", "agecube", "educ", "educsq", "marr",
            "nodegree", "black", "hisp")

fml <- as.formula(paste(
  "re ~ ever_treated * post +",
  paste(X_vars, collapse = " + ")
))

did_add <- lm(fml, data = df_ne_all)
cat(sprintf("DiD with additive X: %.2f\n",
            coef(did_add)[["ever_treated:post"]]))
# Expected: +3,522.47  ← Scott's published number
# Additive X barely helps (naive DiD was +3,621). Need a design-aware estimator.
```

## Outcome regression (Heckman, Ichimura, Todd 1997)

```{r}
wide_ne <- nonexp_panel |>
  filter(year %in% c(75, 78)) |>
  pivot_wider(
    id_cols = c(id, ever_treated, all_of(X_vars)),
    names_from = year, values_from = re, names_prefix = "re"
  ) |>
  mutate(dY = re78 - re75)

or_model <- lm(reformulate(X_vars, response = "dY"),
               data = filter(wide_ne, ever_treated == 0))

treated <- filter(wide_ne, ever_treated == 1)
treated$mu0_hat <- predict(or_model, newdata = treated)
att_or <- mean(treated$dY - treated$mu0_hat)
cat(sprintf("OR ATT: %.2f\n", att_or))
# Expected: +1,604  (≈ $190 below the $1,794 benchmark)
```

## Inverse propensity weighting (Abadie 2005)

```{r}
ps_model <- glm(reformulate(X_vars, response = "ever_treated"),
                data = wide_ne, family = binomial())
wide_ne$p_hat <- predict(ps_model, type = "response")
wide_ne$w <- ifelse(wide_ne$ever_treated == 1, 1,
                    wide_ne$p_hat / (1 - wide_ne$p_hat))

att_ipw <- with(wide_ne,
  mean(dY[ever_treated == 1]) -
  weighted.mean(dY[ever_treated == 0], w = w[ever_treated == 0])
)
cat(sprintf("IPW ATT: %.2f\n", att_ipw))
# Expected: +2,019  (≈ $225 above the $1,794 benchmark; sensitive to overlap)
```

## Doubly-robust DiD (Sant'Anna & Zhao 2020)

```{r}
#| eval: false
# Requires: install.packages("DRDID")
library(DRDID)

drdid_fit <- drdid(
  yname = "re", tname = "year", idname = "id", dname = "ever_treated",
  xformla = ~ age + agesq + educ + educsq + marr + nodegree +
              black + hisp + re74 + u74,
  data = nonexp_panel |> filter(year %in% c(75, 78)),
  panel = TRUE, estMethod = "imp"
)
summary(drdid_fit)
# Expected: ATT ~ +1,959  (≈ $165 above the $1,794 benchmark)
# DR overshoots; OR undershoots. They're roughly tied for closest.
```

## The comparison table (Scott's published `drdid all` output)

| Estimator | ATT | Distance from \$1,794 |
|---|---|---|
| Naive DiD (no $X$)                                  | +\$3,621 | overshoots by \$1,827 |
| DiD with additive $X$ (your `reg` spec)             | +\$3,522 | overshoots by \$1,728 |
| **Design-aware (`drdid all`):**                     |          |          |
| &nbsp;&nbsp;OR — Regression-adjusted (`reg`)        | +\$1,770 | **−\$24** |
| &nbsp;&nbsp;IPW — Abadie (`ipw`)                    | +\$1,861 | +\$67 |
| &nbsp;&nbsp;DR-IPW (`dripw`)                         | +\$1,979 | +\$185 |
| &nbsp;&nbsp;DR-improved (`drimp`)                    | +\$2,033 | +\$239 |
| **RCT benchmark (post-period diff)**                | **+\$1,794** | --- |

Notes:

-   **Additive $X$ barely helps** (\$3,522 vs naive \$3,621). The X main effects don't have the kind of leverage needed to fix mean reversion.
-   **Design-aware estimators all land within \$240** of the benchmark. OR (regression-adjusted) lands closest at \$24 below; DR-improved is furthest at \$239 above.
-   None hit the benchmark exactly — with $n_T = 185$ vs $n_C \approx 16{,}000$, sampling variation alone explains the spread.
-   For the deck's TWFE-with-Post×X spec (id FE + Post × X interactions), the result is +\$1,559 — a different specification with different identification (id FE absorb every time-invariant covariate). That spec belongs in the covariates lesson, not this lab.

## Discussion questions

1.  Which estimators moved the ATT in the right direction? Which got closest?
2.  Drop the Post × X interactions in the TWFE spec — what happens, and why?
3.  Plot the propensity-score overlap: $\widehat p(X)$ density for $D = 1$ vs $D = 0$. Where does overlap fail? What does that imply for IPW and DR?
4.  Why doesn't DR always dominate OR and IPW?
5.  How much of the residual gap is selection on unobservables vs. functional-form misspecification?
